\section*{Personal Background}

\begin{singlespace}
\bi
It is well known that human beings do not receive concrete scores
or reward signals for complex behaviors such as votes in elections.
Current machine learning models remain far below human-level in many
action-oriented tasks, exactly because they require constant, immediate
reward signals\cite{Lake2016}. How can we build machines which learn
to act as fluently as people, according to human-like goals and reasons\cite{Lake2016,Railton2017}?
Recent research among the cognitive sciences has put forth a paradigm
that grips me: weaving together sensorimotor signals into perception,
knowledge, affect, and action\cite{probmods,Clark2013}. I believe
that affect should be taken seriously in artificial intelligence as
well as neuroscience. By pursuing a PhD and subsequent research career,
I am eager to blend the cognitive sciences with computation in investigating
how machines, including ``meat machines'' like us, can evaluate,
reason socially, and pursue goals.
\end{singlespace}

\begin{singlespace}
Arcu volutpat sodales.
Arcu integer pretium orci, vivamus eget libero cursus, metus magna sem sociis lacus ut in.
Et enim tortor, eleifend libero consequat luctus tempora ullamcorper quis, at libero est eu.
At in risus nec et cras sed.
Non ipsum pellentesque pulvinar nulla sit cursus.
Ac vulputate justo ligula felis turpis.
Penatibus ligula lorem dignissim nulla proin, libero auctor ipsum posuere metus egestas temporibus.
\end{singlespace}

\begin{singlespace}
Sed enim vel natoque, mauris in, elementum sapien nulla nec qui vivamus.
Minima praesent, sollicitudin lacinia nam massa, adipiscing lacus, cras suscipit fusce, egestas et luctus praesent ante felis.
Fermentum mauris integer diam et.
Maecenas non luctus donec, ac tincidunt quam amet wisi in dictum, neque bibendum libero vestibulum, aliquam diam.
Risus et id justo sed.
Urna lobortis in leo ac, sagittis ut orci.
In ante cras mi, convallis id, aliquet tincidunt sit dui aenean rutrum wisi, arcu nullam tincidunt, tincidunt dictum.
Nonummy augue ante.
\end{singlespace}
